-----
title: "ANCOVA diet is the indipendent variable and bodyweight the covariate"
output: html_notebook
---
```{r}

setwd("~/Documents/MultiTisssueDiet/linearmodel")
WeightData <- read.csv("~/Documents/MultiTisssueDiet/d_20162021_BXDMultiTissueDiet_Williams_mRNA_DATAwithPhenos.csv",header=F,sep=",", na.strings="")
NewWeightData <- WeightData[, which(colMeans(!is.na(WeightData)) > 0.5)]
NewWeightData <- NewWeightData[ -c(1:3), ]
WData <- as.data.frame (t(NewWeightData))

Samples<-WData[ c(1,2,4,6) ]
Samples[Samples=="CD"]<-0
Samples[Samples=="HF"]<-1
Samples[Samples=="Quadriceps"]<-0
Samples[Samples=="scWAT"]<-1
Samples[Samples=="Intestine"]<-2
Samples[Samples=="Heart"]<-3
Samples[Samples=="Liver"]<-4
Samples[Samples=="BAT"]<-5

NewWData<-cbind(Samples,WData)
NewWData<-NewWData[-c(2,3),-c(5,6,8,10)]
colnames(NewWData) <- NewWData[c(1),]
NewWData <- NewWData[-c(1),]
QWData <- NewWData[NewWData$Tissue == "0",]
sWData <- NewWData[NewWData$Tissue == "1",]
IWData <- NewWData[NewWData$Tissue == "2",]
IWData<-IWData[, which(colMeans(!is.na(IWData)) > 0.5)]
values_count <- sapply(lapply(IWData, unique), length)
IWData = IWData[, values_count > 1]
HWData <- NewWData[NewWData$Tissue == "3",]
LWData <- NewWData[NewWData$Tissue == "4",]

```

```{r}

InputData = IWData

# Anova Diet
AnovaDiet<- vector(mode = "list", length = 17597)
S<- vector( mode = "list",length =  17597)
Di <- vector( length =  17597)
Bo <- vector( length =  17597)
Re <- vector( length =  17597)

for(i in 8: 17597)
{
  AnovaDiet[[i]]= aov( as.numeric(InputData[[i]])~ as.factor(InputData$Diet) + as.numeric(InputData$Bodyweight) , InputData)
  
}


for(i in 8: 17597)
{
  S[i] = summary(AnovaDiet[[i]])
  
}


for(i in 8: 17597)
{
  
  Di[i] = S[[i]]$`Sum Sq`[1]/sum(S[[i]]$`Sum Sq`[1:3])*100
  Bo[i] = S[[i]]$`Sum Sq`[2]/sum(S[[i]]$`Sum Sq`[1:3])*100
  Re[i] = S[[i]]$`Sum Sq`[3]/sum(S[[i]]$`Sum Sq`[1:3])*100
}


Di= as.data.frame(Di)

Re = as.data.frame(Re)

VarExpDiet = cbind(Di,Bo,Re)

rownames (VarExpDiet) = colnames(InputData)
VarExpDiet = as.data.frame(VarExpDiet[-c(1:7),])
write.csv(VarExpDiet, "AnovaVarExDietIntestine.csv")




```

```{r}
#test 1 shuffle
Test = transform(InputData, Bodyweight = sample(Bodyweight),Diet = sample(Diet))
TestData = as.data.frame(Test)


#Anova of shuffled data
TAnovaDiet<- vector(mode = "list", length = 17597)
S<- vector( mode = "list",length =  17597)
TDi <- vector( length =  17597)
TBo <- vector( length =  17597)
TRe <- vector( length =  17597)
for(i in 8: 17597)
{
  TAnovaDiet[[i]]= aov( as.numeric(TestData[[i]])~   as.factor(TestData$Diet) + as.numeric(TestData$Bodyweight) , TestData)
  
}


for(i in 8: 17597)
{
  S[i] = summary(TAnovaDiet[[i]])
  
}


for(i in 8:  17597)
{
  TDi[i] = S[[i]]$`Sum Sq`[1]/sum(S[[i]]$`Sum Sq`[1:3])*100
  TBo[i] = S[[i]]$`Sum Sq`[2]/sum(S[[i]]$`Sum Sq`[1:3])*100
  TRe[i] = S[[i]]$`Sum Sq`[3]/sum(S[[i]]$`Sum Sq`[1:3])*100
}


TDi= as.data.frame(TDi)
TBo= as.data.frame(TBo)

TRe = as.data.frame(TRe)

TVarExpDiet = cbind(TDi,TBo,TRe)

rownames (TVarExpDiet) = colnames(TestData)
TVarExpDiet = as.data.frame(TVarExpDiet[-c(1:7),])
write.csv(TVarExpDiet, "TAnovaVarExDietIntestine.csv")


```


```

```{r}
#create violin plots
require(vioplot)
require(ggplot)
vioplot(VarExpDiet$Di,TVarExpDiet$TDi,VarExpDiet$Bo,TVarExpDiet$TBo,VarExpDiet$Re,TVarExpDiet$TRe ,xlab="variabels", ylab = "variance explained in % ",col=c("blueviolet", "mediumorchid", "royalblue","lightblue", "aquamarine4", "aquamarine") , main = "Violin plots of Variance explained in intestine ", names= c("Diet","Test Diet","Bodyweight","Test Bodyweight","Residuals", "Test Residuals"))
legend("bottomright", fill=c("blueviolet", "mediumorchid", "royalblue","lightblue", "aquamarine4", "aquamarine"), legend=c("Diet real data", "Diet randomized data", "Bodyweight real data", "Bodyweigt randomized data", "Residuals real data","resudials randomized data"))
```


